Precision calculations of the cosmic shear power spectrum projection

### 2017-02-17 limber2.tex
consistent version

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
%
The difference between the second-order Limber and full projection solution using the
spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
for $\vartheta < 200$ arcminutes.}
The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
precision that we can achieve with the current fast Hankel transform implementation
for the correlation function. The green line shows the limit of the
second-order Limber approximation on the correlation function.

>>>>

We compare predictions for the two-point shear correlation function using
the Hankel transformation and the full spherical transformation in
Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
%
We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
%
The difference between the second-order Limber and full projection solution using the
spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
for $\vartheta < 200$ arcminutes.
The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
precision that we can achieve with the current fast Hankel transform implementation
for the correlation function. The green line shows the limit of the
second-order Limber approximation on the correlation function.
